Place of death in NRS COVID-19 deaths: data processing for analysis, 2023 data

### 2023-08-08 covid_nrs_place_of_death_data_2023.Rmd
changed cell ranges in the spreadsheet - they've been updated to only contain 2023 data instead of mix of 2022 & 2023

cell_ranges_for_sex_and_age_data <- list(
  "All" = "A6:K110",
  "Female" = "A113:K217",
  "Male" = "A220:K324"
)

@@

## updated for 2023 which contains both 2022 and 2023
cell_ranges_for_causes_of_death_data <- list(
  "All" = "A6:V110",
  "Care home" = "A113:V217",
  "Home & other non-institution" = "A220:V324",
  "Hospital" = "A327:V431",
  "Other" = "A434:V538"
)

## this was for only 2022 data
# cell_ranges_for_causes_of_death_data <- list(
#   "All" = "A6:V58",
#   "Care home" = "A61:V113",
#   "Home & other non-institution" = "A116:V168",
#   "Hospital" = "A171:V223",
#   "Other" = "A226:V278"
# )

>>>>

# TODO: the data have changed again, now the most recent file no longer includes 2022 and 2023, but only 2023, so the cell ranges below are inaccurate and result in errors!
# 
# cell_ranges_for_sex_and_age_data <- list(
#   "All" = "A6:K110",
#   "Female" = "A113:K217",
#   "Male" = "A220:K324"
# )
cell_ranges_for_sex_and_age_data <- list(
  "All" = "A6:K58",
  "Female" = "A61:K113",
  "Male" = "A116:K168"
)

@@

## updated for 2023 which contains both 2022 and 2023
# cell_ranges_for_causes_of_death_data <- list(
#   "All" = "A6:V110",
#   "Care home" = "A113:V217",
#   "Home & other non-institution" = "A220:V324",
#   "Hospital" = "A327:V431",
#   "Other" = "A434:V538"
# )

## this was for only 2022 data
## ...and is correct again for 2023
cell_ranges_for_causes_of_death_data <- list(
  "All" = "A6:V58",
  "Care home" = "A61:V113",
  "Home & other non-institution" = "A116:V168",
  "Hospital" = "A171:V223",
  "Other" = "A226:V278"
)
